% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
\usepackage{fancyhdr}
\pagestyle{fancy} 

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
%\setlength{\textheight}{9.5in} % sincrease text height to fit on 1-page 


\begin{document} 

\name{Mark H. Spatz\\[8pt]}     % the \\[12pt] adds a blank
				        % line after name      

\address{mspatz@mit.edu\\mark.h.spatz@gmail.com  }
\address{(816)-679-1502}

%\renewcommand{\headrulewidth}{0pt} %delete hrule under name
\cfoot{References Available upon Request}                                  
\begin{resume}
        
\section{Education}
\vspace{0.05in} 

{\bf May 2014:} B.S. in Electrical Science and Engineering, Massachusetts Institute of Technology\\
{\bf December 2016:} M.S. in Electrical Science and Engineering, Massachusetts Institute of Technology
\section{Coursework}
	\vspace{0.05in}
	{\bf Spring 2016} 6.776: High Speed Communication Circuits, 8.044: Statistical Physics I\vspace{0.05in}\\
	{\bf Fall 2015} 6.556: Data Acquisition and Image Reconstruction in MRI, 18.06: Linear Algebra\vspace{0.05in}\\
    {\bf Spring 2014} 6.101: Analog Circuits Lab, 6.006: Introduction to Algorithms \vspace{0.05in}\\
    {\bf Fall 2013} 6.301: Solid State Circuits, 6.332: Advanced Topics in Power Electronics, Chinese I \vspace{0.05in}\\
    {\bf Spring 2013} 6.302: Feedback Systems, 6.334: Power Electronics, 6.011: Intro to Communication, Control, and Signal Processing \vspace{0.05in}\\
    {\bf Fall 2012} 6.013: Electromagnetics and Applications, 6.003: Signals and Systems, 6.041 Probabilistic Systems Analisys \vspace{0.05in}\\
    {\bf Spring 2012} 6.012: Microelectronic Devices \& Circuits, 6.004: Computation Structures \vspace{0.05in}\\
    {\bf Fall 2011}  6.02: Intro to EECS II, 6.002: Circuits \& Electronics, 6.131: Power Electronics Lab\vspace{0.05in}\\    
    {\bf Spring 2011} 6.01: Intro to EECS I, 18.03: Differential Equations
\section{Experience}
	\vspace{0.05in}
	{\bf Research Assistant, Magnetic Resonance Imaging Group. September 2015 - Present:} Building a 128 channel MRI receive coil for fetal imaging. \vspace{0.05in}\\
	{\bf Electrical Engineer, SQZ Biotech. June-August 2015:} Developed a pressure control system to drive material through microfluidic chips. \vspace{0.05in}\\
	{\bf Electrical Engineer, Ashton Instruments. February-May 2015:} Created a development board for an upcoming bicycle power meter.  Created/maintained various pieces of firmware and data analysis software. \vspace{0.05in}\\
	{\bf iPad Systems EE Intern, Apple Inc. June-December 2014:} Worked on the systems integration team facilitating pre-production iPad builds, troubleshooting production and desense issues, and completing characterization tasks.\vspace{0.05in}\\
	{\bf Research Intern, Fitbit Inc. Summer 2013:} Developed a new pedometer algorithm for internal verification purposes and did investigative work on the electronics for a new product.\vspace{0.05in}\\
	{\bf Production Intern, Fitbit Inc. Summer 2012:} Helped with preliminary FCC testing for the fitbit One, and spent a total of four weeks in mainland China helping bring up production lines for the fitbit Zip.\\
\section{Interests and Skills}
\begin{itemize}

  \item Circuit design and debugging
  \item PCB design, mostly using KiCad
  \item Switching converters and other power electronics
  \item ARM and AVR development
  \item Proficient in C, Python, and Matlab.
\end{itemize}

\end{resume}
\end{document}
